\plaintitle

### 2017-06-06 papers/IoT2017/services.tex
no message

In this subsection, we describe the services on which transactions are built and which build on transactions.
We have already discussed distributed ledgers, which permanently store transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build all other services within our system.
Without this communication layer, transactions and bids could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
We must provide prosumers with the ability to create and publish transactions anonymously.
More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.

@@

However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
\begin{itemize}
\item If a prosumer wishes to sell energy, it must first withdraw an energy asset from its smart meter using a blockchain transaction.
This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
\item If a prosumer wishes to buy energy, it must first withdraw an energy consumption asset from its smart meter in a way similar to withdrawing an energy production asset.
\end{itemize}

>>>>

In this subsection, we describe the various services that are implemented in our system. %on which transactions are built and which build on transactions.
We have already discussed the distributed ledger, which permanently stores valid transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.\Aron{Revise list based on final organization!}

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build all the other services in our system.
Without this communication layer, transactions and bids could be easily de-anonymized based on their sources' network identifiers (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
Fortunately, most distributed ledgers allow users to easily generate new addresses\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum. 
Specifically, we use the term address to denote a possible destination for asset transfers. 
Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
at random.
Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.

To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
In practice, a mixing service can be implemented using multiple approaches.
The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party, which would constitute a single point of failure.
Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.

\begin{comment}
We must provide prosumers with the ability to create and publish transactions anonymously.
More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.

@@

However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
\begin{itemize}
\item If a prosumer wishes to sell energy, it must first withdraw an energy asset from its smart meter using a blockchain transaction.
This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
\item If a prosumer wishes to buy energy, it must first withdraw an energy consumption asset from its smart meter in a way similar to withdrawing an energy production asset.
\end{itemize}
\end{comment}

### 2017-06-06 papers/IoT2017/transactions.tex
no message

An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
\begin{compactitem}
\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
\item All of the signatures are valid, which ensures that only the current owner can transfer an asset.
\item For each asset type (and for each timestep), the sum of inputs and outputs is equal.
For example, in the case of energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
%
%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
\end{align*}
%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
The conditions for consumption and financial assets can be described formally in similar ways.
\end{compactitem}
%If a transaction submitted to the ledger is valid, it will be permanently recorded.

@@

\Aron{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
A transaction is valid if the following two conditions hold.
\begin{compactitem}
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
\item The smart meter's signature is valid (for public key, see regulatory transactions).
\end{compactitem}

@@

The DSO uses regulatory transactions for two purposes: to manage authorized smart meters and to set a price policy.
First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
Whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if %the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and % specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
Similarly, later regulatory transactions recorded on the ledger override the authorization and bans of earlier transactions.

>>>>

An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
\item All of the signatures are valid, which ensures that only the current owner can transfer an asset.
\item For each asset type (and for each timestep), the sum of inputs and outputs is equal.
For example, in the case of energy production assets, the condition is
\begin{align*}
& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
%
%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
\end{align*}
%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
The conditions for consumption and financial assets can be described formally in similar ways.
\end{itemize}
%If a transaction submitted to the ledger is valid, it will be permanently recorded.

@@

\Aron{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
A transaction is valid if the following two conditions hold.
\begin{itemize}[noitemsep,topsep=-\parskip]
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
\item The smart meter's signature is valid (for public key, see regulatory transactions).
\end{itemize}

@@

The DSO uses regulatory transactions for two purposes: to manage the set of authorized smart meters and to change the price policy.
%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
First, whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.

@@

A regulatory transaction of this type is valid if %the following two conditions hold:
%\begin{compactitem}
%\item 
\field{timestep} is not in the past and % specified in the transaction is in the future.
%\item 
the DSO's signature is valid.
%\end{compactitem}
%
The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
Similarly, regulatory transactions that are recorded on the ledger later override the authorizations and bans of earlier transactions.
